```{r setup, include=FALSE}
library(tidyverse)    #1.3.1
library(readxl)       #1.3.1
library(ggplot2)      #3.3.3
library(skimr)        #2.1.3
library(here)         #1.0.1
library(pagedown)     #0.14
library(fs)           #1.5.0
library(DBI)          #1.1.1
library(RPostgreSQL)  #0.6-2
library(remotes)      #2.4.0
library(RPostgres)    #1.3.2
library(phyloseq)     #1.34.0
library(knitr)        #1.33
library(stringr)      #1.4.0
library(plotly)       #4.9.4
library(shiny)        #1.6.0
library(tidyr)        #1.1.3
library(vegan)        #2.5-7
library(VennDiagram)  #1.6.20
library(lme4)         #1.1-27
library(phangorn)     #2.7.0
library(bookdown)     #0.22
```

# Guerrilla analytics{-}
================================================================================

>__About the exercise__

<br> 
During this exercise I learned about the Guerrilla Analytics Principles. I also added a proper folder structure to all my projects.

***


>__A__

- _Look at your RStudio project that you created for the DAUR-II final assignment_
- _Rearrange your project according the Guerilla principles explained above_
- _Add README files to the datasets_
- _Use the {fs} package to share a screenshot of your folder tree in your portfolio, look [here](https://www.tidyverse.org/blog/2018/01/fs-1.0.0/) for more info on how to use the {fs} package._

```{r folder structure, warning=FALSE}
library(fs)
dir_tree(path = ".")
```
