```{r setup, include=FALSE}
library(tidyverse)    #1.3.1
library(readxl)       #1.3.1
library(ggplot2)      #3.3.3
library(skimr)        #2.1.3
library(here)         #1.0.1
library(pagedown)     #0.14
library(fs)           #1.5.0
library(DBI)          #1.1.1
library(RPostgreSQL)  #0.6-2
library(remotes)      #2.4.0
library(RPostgres)    #1.3.2
library(phyloseq)     #1.34.0
library(knitr)        #1.33
library(stringr)      #1.4.0
library(plotly)       #4.9.4
library(shiny)        #1.6.0
library(tidyr)        #1.1.3
library(vegan)        #2.5-7
library(VennDiagram)  #1.6.20
library(lme4)         #1.1-27
library(phangorn)     #2.7.0
library(bookdown)     #0.22
```

# Relational databases{-}
================================================================================

>__About the exercise__

<br> 
In this exercise I learned about SQL and database-skills. firstly, the data was imported from [this](https://github.com/DataScienceILC/tlsc-dsfb26v-20_workflows) GitHub page. After that the data is manipulated in such a way that the 3 datasets can be merged together. At last the data is visualized in 3 different plots.


***
>__A__

_Load the flu (“./data/flu_data.csv), the dengue (.”/data/dengue_data.csv) and the gapminder ({dslabs} package) into three separate dataframes in R_

```{r Relational databases A}
#Load the flu dataset
flu_data_import <- read.csv("data/flu_data.csv", skip = 11)
#Load the dengue dataset
dengue_data_import <- read.csv("data/dengue_data.csv", skip = 11)
#Load the gapminder dataset
gapminder <- dslabs::gapminder
```


***
>__B__

_Check if they are in the right shape. Is the data in the ‘tidy’ format? If not change the format to ‘tidy’_

```{r Relational databases B}
#Make flu_data tidy
flu_data_tidy <- flu_data_import %>% tidyr::pivot_longer(cols = Argentina:Uruguay,
                      names_to = "country", 
                      values_to = "value")
#Make dengue_data tidy
dengue_data_tidy <- dengue_data_import %>% tidyr::pivot_longer(cols = Argentina:Venezuela,
                      names_to = "country", 
                      values_to = "value")
```

***
>__c__

_Change the country and date variables of the three tables so that they coincide in terms of data type, class and values_

```{r Relational databases C}
##FLU DATASET
#Seperate the flu date
flu_data_equal <- flu_data_tidy %>% separate("Date", into = c("year", "month", "day"), sep = "-") 
#Change the data type
flu_data_equal$year <- as.integer(flu_data_equal$year)
flu_data_equal$country <- as.factor(flu_data_equal$country)
#Delete the day and month column 
flu_data_equal <- flu_data_equal[-c(2,3)]


##DENGUE DATASET
#Seperate the dengue date
dengue_data_equal <- dengue_data_tidy %>% separate("Date", into = c("year", "month", "day"), sep = "-") 
#Change the data type
dengue_data_equal$year <- as.integer(dengue_data_equal$year)
dengue_data_equal$country <- as.factor(dengue_data_equal$country)
#Delete the day and month column
dengue_data_equal <- dengue_data_equal[-c(2,3)] 
```
***
>__D__

_Store the three tables as separate (so six in total) .csv and .rds files._

```{r Relational databases D}
#Store the files as .csv
write.csv(flu_data_equal, "data/flu_data_equal.csv", row.names = FALSE)
write.csv(dengue_data_equal, "data/dengue_data_equal.csv", row.names = FALSE)
write.csv(gapminder, "data/gapminder.csv", row.names = FALSE)
#Store the files as .rds
saveRDS(flu_data_equal, "data/flu_data_equal.rds")
saveRDS(dengue_data_equal, "data/dengue_data_equal.rds")
saveRDS(gapminder, "data/gapminder.rds")
```



***
>__E__

_In Dbeaver create a new PostgreSQL database “workflowsdb”_

```{r Relational databases connection E, eval=FALSE}
#I left out my password, therefore the code will not work. If you have Postgres you can fill in your own details. 
#Delete every, eval=FALSE from the headliners of the chunk. Than this Rmarkdown file will work.
con <- dbConnect(RPostgres::Postgres(), 
                 dbname = "myfirstdb", 
                 host="localhost", 
                 port="5432", 
                 user="postgres", 
                 password="xxx") 

```


***
>__F__

_Using RPostgreSQL, insert the tables into the database._

```{r Relational databases F, eval=FALSE}
dbWriteTable(con, "dengue_data_db", dengue_data_equal, overwrite = T)
dbWriteTable(con, "flu_data_db", flu_data_equal, overwrite = T)
dbWriteTable(con, "gapminder_db", gapminder, overwrite = T)

```

***
>__G__

_Inspect the contents of the tables with SQL (in DBeaver) and save the SQL script._

```{sql, eval=FALSE}
SELECT *  FROM "dengue_data_db";
SELECT *  FROM "flu_data_db";
SELECT *  FROM "gapminder_db";
```


***
>__H__

_Inspect the contents of the tables with dplyr (in R) and save a RMarkdown showing what you are doing._

```{r Relational databases H, eval=FALSE}
db_names <- c("flu_data_db", "dengue_data_db", "gapminder_db")
databases <- list()
for (x in db_names){
   databases[[paste(x)]] <- dbReadTable(con, x)
}
#inspect the data
#databases[1]
#databases[2]
#databases[3]

```


***
>__I__

_Load the gapminder data in R and change the dataframe in such as way that you could join it to dengue and flue._


```{r Relational databases I, eval=FALSE}
#Filter the year of gapminder_db from 2002 to 2015, so it will fit the data format of dengue and flue
gapminder_change <- databases[3] %>% as.data.frame()
gapminder_filter <- gapminder %>% filter(between(year, 2002, 2015)) 

```

***
>__J__

_Save this clean gapminder data in the “workflowsdb” database_

```{r Relational databases J, eval=FALSE}
dbWriteTable(con, "gapminder_filter", gapminder_filter, overwrite = T)

```


***
>__K__

_Perform some joins (your choice) with SQL (can be done in DBeaver or with dplyr._

```{r joining the tables, eval=FALSE}
#Combine all the tables with left_join
data_dengue_flu <- left_join(dengue_data_equal, flu_data_equal, by = c("country", "year"))
data_all_tables <- left_join(data_dengue_flu, gapminder_filter, by = c("country", "year"))


```


***
>__L__

_Generate a joined table, and export this from the database to R._
<br>
The combined dataframe is already in R (called data_all_tables)

***
>__M__

_Show some descriptive statistics with this table, and at least 3 visualisations using ggplot2._

```{r Relational databases M, plot 1, eval=FALSE}
#Plot 1, show the fertility over the past years in America
fertility_america <- data_all_tables %>% filter(continent == "Americas") %>% select(fertility, year)
fertility_america

#Filter countries on Brazil, Mexico and Bolivia
data_3_countries <- data_all_tables %>% filter(country == c("Brazil", "Mexico", "Bolivia"))

  
  
  #Plot1, life expectancy in the continents
ggplot(data_3_countries, aes(x = country, y = life_expectancy)) +
  geom_boxplot(aes(fill = country),
    outlier.colour = "black") + 
  labs(title = "Boxplot of the life expectancy in Brazil, Mexico and Bolivia",
       y = "life expectancy",
       x = "")
```

```{r Relational databases M, plot 2, eval=FALSE}
#plot 2, show the flu data over the past few years in the continent America
flu_america <- data_all_tables %>% filter(continent == "Americas") %>% select(value.x, year)

ggplot(data=flu_america) +
  geom_col(aes(x = year, y = value.x, fill = year), show.legend = FALSE) +
           labs(title = "Bar graph of the flu data over the years in America",
                y = "")
```

```{r Relational databases M, plot 3, eval=FALSE}
#plot 3, line graph of the dengue data in azia over the years
dengue_America <- data_all_tables %>% filter(continent == "Americas") %>% select(infant_mortality, year)

ggplot(data = dengue_America) +
  geom_col(aes(x = year, y = infant_mortality, fill = year), show.legend = FALSE)+ scale_fill_gradient(low="red", high="yellow") +
  labs(title = "Bar graph of the infant mortality in America over the past years", 
       y = "infant mortality")

```
***
>__N__

_show all of your actions in this assignment in a Rmd file, perhaps with pictures and provide text explaining and showcasing your skills._



