
# COVID-19 parameterized report{-}
================================================================================

>__About the exercise__

<br> 
In this exercise I will create a parameterized report of COVID-19 cases and deaths. The data used in this exercise can be found [here](https://www.ecdc.europa.eu/en/publications-data/data-daily-new-cases-covid-19-eueea-country). This data will be filtered on the different parameters, these are: 

Params | Explanation
------------- | ------------- 
Data | The location of the file that should be used
Country | Which country to filter on
Day | Day of the first date to work with
Month | Month of the first date to work with
Year | Year of the first date to work with

The params can be filled in in the index.Rmd. the first date that can be used is 2-3-2021.


```{r loading and manipulating the data}
#Set this option in the first code chunk
knitr::opts_chunk$set(echo = params$printcode)

#Loading the data given by a param 
COVID_data <- read.csv(params$data)

#filter on country given by a param
COVID_country <- COVID_data %>% filter(countriesAndTerritories == params$country)

#getting the rownumber of the given params (day, month, year)
row_number <- which((COVID_country$day == params$day) & (COVID_country$month == params$month) & (COVID_country$year == params$year))

#Filter the COVID_country from the first line to row_number
COVID_filter <- COVID_country[1:row_number, ]

#replace date column to date class
COVID_filter$dateRep <- as.Date(COVID_filter$dateRep,
                                format = "%d/%m/%y")
```

```{r covid cases}
#Creating a variable with the country name
country <- params$country
#Plotting the graph
COVID_filter %>% ggplot() +
  geom_line(aes(x = dateRep, y = cases), color = "red") +
  theme_classic() +
  labs(title = paste("recorded COVID-19 cases in", country),
       x = "")
```

```{r covid deaths}
#Plotting the graph
COVID_filter %>% ggplot() +
  geom_line(aes(x = dateRep, y = deaths), color = "red") +
  theme_classic() +
  labs(title = paste("Recorded COVID-19 deaths in", country),
       x = "")
```